\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2021-02-28 manuscript.Rnw
Minor edits to cDTSTM math notation

\subsection{Cohort discrete time state transition models} \label{sec:cDTSTMs}
cDTSTMs simulate the probability that a cohort of patients is in each of $H$ health states over time. Time is partitioned into intervals $\{[0, t_1], [t_1, t_2], \ldots, [t_C, t_{C+1}]\}$ with each interval $0,\ldots, C$ referred to as a model cycle. We denote $t_c$ as the time at the start of model cycle $c$. An $H \times 1$ state vector that stores the probability of being in each health state at cycle $c$ is written as $x_c = (x_{1c}, x_{2c}, \ldots, x_{Hc})$ where $\sum_h x_{hc} = 1$. A transition probability matrix is an $H \times H$ matrix denoted by $P_c$ where the $(r,s)$th element represents a transition from state $r$ to state $s$ between model cycles $c$ and $c+1$. The state vector at cycle $c+1$ for each of $C$ model cycles is given by,

\begin{equation} \label{eqn:markov-sim}
x_{c+1}^T= x_c^T P_c, \quad c = 0,\ldots, C.
\end{equation}

@@

\begin{equation} \label{eqn:riemann-sum}
\sum_{c = 0}^{C}f(t_c^{*})\Delta t_c,
\end{equation}

where $\Delta t_c = t_{c+1} - t_{c}$,  $t_c^{*}\in[t_{c},t_{c+1}]$, and $f(t)= z_h(t) e^{-rt} p_h(t)$. Three methods can be used to estimate $f(t_c^{*})$. First, a left Riemann sum uses values at the start of each time interval, $f(t_c^{*}) = f(t_c)$. Second, a right Riemann sum uses values at the end of each time interval, $f(t_c^{*}) = f(t_{c+1})$. Finally, the trapezoid rule averages values at the start and end of each interval, $f(t_c^{*}) = \frac{1}{2}\Delta t_c[f(t_c) + f(t_{c+1})]$.

>>>>

\subsection{Cohort discrete time state transition models} \label{sec:cDTSTMs}
cDTSTMs simulate the probability that a cohort of patients is in each of $H$ health states over time. Time is partitioned into intervals $\{[0, t_1], [t_1, t_2], \ldots, [t_{C-1}, t_C]\}$ with each interval $1,\ldots, C$ referred to as a model cycle. We denote $t_c$ as the time at the end of model cycle $c$. An $H \times 1$ state vector that stores the probability of being in each health state at cycle $c$ is written as $x_c = (x_{1c}, x_{2c}, \ldots, x_{Hc})$ where $\sum_h x_{hc} = 1$. A transition probability matrix is an $H \times H$ matrix denoted by $P_c$ where the $(r,s)$th element represents a transition from state $r$ to state $s$ between model cycles $c$ and $c+1$. The state vector at cycle $c+1$ for each of $C$ model cycles is given by,

\begin{equation} \label{eqn:markov-sim}
x_{c+1}^T= x_c^T P_c, \quad c = 0,\ldots, C-1.
\end{equation}

@@

\begin{equation} \label{eqn:riemann-sum}
\sum_{c = 1}^{C}f(t_c^{*})\Delta t_c,
\end{equation}

where $\Delta t_c = t_{c} - t_{c-1}$,  $t_c^{*}\in[t_{c-1},t_{c}]$, and $f(t)= z_h(t) e^{-rt} p_h(t)$. Three methods can be used to estimate $f(t_c^{*})$. First, a left Riemann sum uses values at the start of each time interval, $f(t_c^{*}) = f(t_{c-1})$. Second, a right Riemann sum uses values at the end of each time interval, $f(t_c^{*}) = f(t_{c})$. Finally, the trapezoid rule averages values at the start and end of each interval, $f(t_c^{*}) = \frac{1}{2}\Delta t_c[f(t_{c-1}) + f(t_{c})]$.
